{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-09-09 documents/application.tex
Turbidimeter actually working now

@@

Considering the electric field skin depth of average lung tissue\cite{gabriel1996compilation} (which changes considerably based on )

@@

6 cm of l

The

Fat and

The penetration of microwave power is very sensitive to

>>>>

High microwave frequencies are very strongly attenuated by tissue. However, we have a large amount of margin in the electric field - 4 orders of magnitude - that we can trade for penetration depth.

\cite{neuroinvasive2020} \cite{situ2020}

@@

Considering only the electric field skin depth\cite{Safety2001}\cite{Physical1982} of average lung tissue\cite{gabriel1996compilation}\cite{Dielectricb}\cite{Dielectric}\cite{Tissue2018} (which changes considerably based on inflation), on the face of it is possible to achieve a field of 150 V/m at a very reasonable depth of 60 mm. We could not find any data on the distribution of gas exchange throughout the cross-section of the lung; however,

@@
